NGO analysis

### 2022-07-26 Shiny/Test/Dashboard downloads test.Rmd
Adding a download notification.

output$report <- downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

>>>>

output$report <- downloadHandler(

  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

    id <- showNotification(
      "Generating report...",
      duration = NULL,
      closeButton = FALSE
    )
    on.exit(removeNotification(id), add = TRUE)
